\section{Deriving the Metropolis Hasting acceptance ratio}
\label{appendix:MH_ratio}

\subsection{Updating the opportunity set}

Target distribution for a firm $i$ 

\begin{align}
p(O_i | A_i, \alpha, \bm{\beta}) &= \frac{p(O_i, A_i, \alpha, \bm{\beta})}{p(A_i, \alpha, \bm{\beta})}
\end{align}

We propose a new $O_i^*$ by randomly sample a new offer, $j^*$ for each firm. If the new offer is not already in the current opportunity set, we add the offer to the set. If it already is in the opportunity set, we remove it from the set.

We then calculate the Metropolis-Hasting acceptance ratio:

\begin{align}
MH_O = \frac{p(O_i^* | A_i, \alpha, \bm{\beta})}{p(O_i | A_i, \alpha, \bm{\beta})} &= \frac{p(O_i^*, A_i, \alpha, \bm{\beta})}{p(A_i, \alpha, \bm{\beta})} \times \frac{p(A_i, \alpha, \bm{\beta})}{p(O_i, A_i, \alpha, \bm{\beta})} \\
&= \frac{p(O_i^*, A_i, \alpha, \bm{\beta})}{p(O_i, A_i, \alpha, \bm{\beta})} \\
&= \frac{p(A_i | O_i^*, \alpha)p(O_i^*|\bm{\beta})}{p(A_i | O_i, \alpha)p(O_i|\bm{\beta})} \label{eq:updateO_joint_dist_into_conditional_dist} \\
\end{align}

where the factorization of the likelihood in \Cref{eq:updateO_joint_dist_into_conditional_dist} is due to the fact that the acceptance of firm $i$ only depends on what is offered to it and what is its preference, $p(A_i | O_i^*, \alpha)$; what is offered to $i$ depends on the preferences of all countries, $p(O_i^* \ \bm{\beta})$.

If we plug in \Cref{eq:conditional_probability_of_accept} and \Cref{eq:conditional_probability_of_offer}

\begin{align}
\frac{p(O_i^* | A_i, \alpha, \bm{\beta})}{p(O_i | A_i, \alpha, \bm{\beta})} &= \frac{\sum\limits_{j:j \in O_i} \exp(\alpha'W_j)}{\sum\limits_{j:j \in O_i} \exp(\alpha'W_j) + \exp(\alpha' W_{j^*})} \times \exp(\bm{\beta}_{j^*}'X_i)
\end{align}

where $j^*$ is the index of the newly sampled job. This is the case when the newly proposed job is not already offered, so it's added to the opportunity set.

When the newly proposed job is already offered, so it's removed from the opportunity set, we have

\begin{align}
\frac{p(O_i^* | A_i, \alpha, \bm{\beta})}{p(O_i | A_i, \alpha, \bm{\beta})} &= \frac{\sum\limits_{j:j \in O_i} \exp(\alpha'W_j)}{\sum\limits_{j:j \in O_i} \exp(\alpha'W_j) - \exp(\alpha' W_{j^*})} \times -\exp(\bm{\beta}_{j^*}'X_i)
\end{align}

\subsection{Updating firms' parameters, $\alpha$}

Target distribution:

\begin{align}
p(\alpha | A, O, \bm{\beta}) &= \frac{p(O, A, \alpha, \bm{\beta})}{p(A, O, \bm{\beta})}
\end{align}

We propose a new $\alpha^*$ using a symmetric proposal distribution that sample $\alpha^*$ in a box whose boundary is $\alpha^* \pm \epsilon_\alpha$

Metropolis-Hasting acceptance ratio:

\begin{align}
MH_\alpha = \frac{p(\alpha^* | A, O, \bm{\beta})}{p(\alpha | A, O, \bm{\beta})} &= \frac{p(A_i | O_i, \alpha^*)p(O_i|\bm{\beta})}{p(A_i | O_i, \alpha)p(O_i|\bm{\beta})} \\
&= \frac{p(A_i | O_i, \alpha^*)}{p(A_i | O_i, \alpha)} \label{eq:updatealpha_MHratio_final}
\end{align}

where \Cref{eq:updatealpha_MHratio_final} is due to the flat prior (so $\frac{p(\alpha^*)}{p(\alpha)}=1$) and the symmetric proposal distribution (so $\frac{p(\alpha^*|\alpha)}{p(\alpha|\alpha^*)} = 1$)

If we plug in \Cref{eq:conditional_probability_of_accept},

\begin{align}
MH_\alpha &= \prod_i \left[ \frac{\exp(\alpha^{*\prime} W_{a_i})}{\exp(\alpha' W_{a_i})} \times \frac{\sum\limits_{j:j \in O_i} \exp(\alpha' W_j)}{\sum\limits_{j:j \in O_i} \exp(\alpha^{*\prime}W_j)} \right] \\
&= \prod_i \left[ \exp(\epsilon_\alpha ' W_{a_i}) \times \frac{\sum\limits_{j:j \in O_i} \exp(\alpha' W_j)}{\sum\limits_{j:j \in O_i} \exp(\alpha^{*\prime}W_j)} \right]
\end{align}

Finally, we log transform the MH acceptance ratio for numerical stability.

\begin{align}
\log MH_\alpha &= \sum_i \left[ \epsilon_\alpha' W_{a_i} + \log\left(\sum\limits_{j:j \in O_i} \exp(\alpha' W_j)\right) - \log\left(\sum\limits_{j:j \in O_i} \exp(\alpha^{*\prime} W_j)\right) \right]
\end{align}

\subsection{Updating countries' parameters, \texorpdfstring{$\boldmath\beta$}{}}

Target distribution:

\begin{align}
p(\bm{\beta}|A, O, \alpha) &= \frac{p(O, A, \alpha, \bm{\beta})}{p(A, O, \alpha)}
\end{align}

We propose a new $\bm{\beta}^*$ using a symmetric proposal distribution that sample $\bm{\beta}^*$ in a box with side length $\epsilon_\beta$

Metropolis-Hasting acceptance ratio:

\begin{align}
MH_\beta = \frac{p(\beta^* | A, O, \alpha)}{p(\beta | A, O, \alpha)} &= \frac{p(A_i | O_i, \alpha)p(O_i|\bm{\beta}^*)}{p(A_i | O_i, \alpha)p(O_i|\bm{\beta})} \label{eq:updatebeta_MHratio_simplify} \\
&= \frac{p(O_i|\bm{\beta}^*)}{p(O_i|\bm{\beta})} \label{eq:updatebeta_MHratio_final}
\end{align}

where \Cref{eq:updatebeta_MHratio_simplify} is due to the flat prior on $\beta$ and the symmetric proposal distribution.

We plug in \Cref{eq:conditional_probability_of_offer},

\begin{align}
MH_\beta &= \prod_i \left[ \prod\limits_{j \in O_j}\frac{ \exp(\beta_j^{*\prime}X_i)}{ \exp(\beta_j^{\prime}X_i)} \times \prod\limits_{j}\frac{1 + \exp(\beta_j^{*\prime}X_i)}{1 + \exp(\beta_j^{\prime}X_i)} \right] \\
\log MH_\beta &= \sum_i \left[ \sum_{j \in O_i} \beta_j^{*\prime}X_i - \beta_j^{\prime}X_i + \sum_{j} \log(1 + {\exp({\beta_j^{*\prime}X_i})) - \log(1 +  \exp(\beta_j^{\prime}X_i})) \right]
\end{align}

In the MCMC implementation, since $\bm{\beta}$ is high dimensional, we conduct multiple block Metropolis Hastings, updating several $\beta$'s at one time.