\section{Applying the Two-Sided Matching Model to Japanese MNCs}
\label{sec:application}

In this section, I apply the two-sided matching model to study the investment location of Japanese firms overseas. The data comes from the \textit{Kaigai Shinshutsu Kigyou Souran}, an annual publication that contains information about the foreign affiliates of Japanese firms, including their location, industry, capital, and labor size.\footnote{I thank Professor Andrew Delios for generously sharing the data.} This database is reputed to include all Japanese firms overseas \citep{Yamawaki1991}. The final sample includes 6474 Japanese foreign affiliates in 2003, spreading across 37 countries, with China and the US leading as the two top destinations for Japanese MNCs (\Cref{tab:list_of_countries}).

For countries' characteristics that firms consider, I include:

\begin{itemize}
\item Market size: MNCs are expected to prefer countries with a large market size, which present MNCs with many potential customers. Indeed, this has been often cited as the allure of China to MNCs \citep{Luo2010}. I follow the standards in the literature and include log GDP (constant 2005 US\$), taken from the World Bank's World Development Indicators.

\item Level of development: MNCs are expected to prefer countries with a high level of development. A developed economy has consumers with high purchasing power and better infrastructure. To measure development, I use log GDP per capita (constant 2005 US\$) from World Development Indicators.

\item Labor quality: As one primary factor of production, labor matters greatly to firms' productivity and profit. To measure labor quality, I use the average years of schooling of adult, taken from the UNDP's Human Development Report.\footnote{Since Taiwan is not included in UNDP's and World Bank's data, I collected its statistics from the Taiwanese Statistical Website.}

\item Democracy: Democracy has been a mainstay in the political science literature on FDI. Scholars have argued that MNCs want to invest in democratic regimes for various reasons, including stable policy, credible commitment, and strong property rights \citep{Ahlquist2006, Li2003, Jensen2003}. On the other hand, recent works have also argued that democratic regimes want FDI more than autocratic regimes \citep{Pandya2016}. Thus, it is unclear whether the observed high level of FDI in democracies is due to the push or the pull factors. By controlling for countries' preference in the two-sided matching model, I can better estimate the effect of democracies on firms' utility. I measure democracy using the binary Demoracy \& Dictatorship, developed by \citet{Cheibub2009b}.
\end{itemize}

For firms' characteristics that countries consider, I include:

\begin{itemize}
\item Capital size (in US\$): A main argument for the benefit of FDI is that it brings capital to the country, improving labor productivity. MNCs' capital is especially important for developing countries, which cannot muster much domestic capital from their poor population. The capital size of a firm is included in the Japanese Overseas Business dataset.

\item Labor size: Similarly, a reputed benefit of FDI is that it creates jobs, generating not just economic growth but also increasing the government's popularity among the populace. The total number of employees of a firm is included in the Japanese Overseas Business dataset.

\item Technology intensity: I proxy for a firm's technology intensity by the industry to which it belongs. \citet{OECD2009} categorizes ISIC industries into four levels of technology intensity---low, medium low, medium high, and high---according to the level of R\&D expenditure divided by sales. I convert the industry classification of firms in my data from SIC 3 to ISIC and categorize their technology intensity from 1 to 4, with 1 being low and 4 being high. On several occasions, one industry in SIC 3 matches to multiple ISIC (rev 3) industries or none at all. In the former case, I take the average across matched ISIC industries. In the latter case, the data is missing and later removed from the analysis.
\end{itemize}